\documentclass[]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage[nonumber, contents]{cuisine}
\RecipeWidths{\textwidth}{1cm}{.2cm}{4cm}{1.5cm}{1cm}

\begin{document}

\tableofcontents
\newpage


\section{Food}

\subsection{Mexican}

\begin{recipe}{Barbacoa}{}{}
	
	
	\ing[2-4]{lbs}{beef chuck roast}
	Coat all sides of the roast with kosher salt. Cover and refridgerate overnight or for
	at least an hour.
	
	\newstep
	Preheat oven to 275\0F. Adjust rack to lower-middle position.
	
	\ing[10]{g}{dried chile negro}
	\ing[5]{g}{dried chile pasilla}
	\ing[5]{g}{dried chile morita}
	Discard the stems and seeds and add the chiles to a heavy-bottomed Dutch oven.
	Cook over medium-high heat, stirring/turning frequently, until they have an intense
	roasted aroma, 2 to 5 minutes. Don't allow to smoke.

	\ing[2]{cups}{chicken stock}
	Add roasted chiles to a microwave-safe bowl and add 2 cups of the chicken stock.
	Cover with plastic wrap and microwave on high power for 5 minutes.

	\ing[25]{g}{garlic (smashed)}
	\ing[250]{g}{onion (finely sliced)}
	\ing[2]{tbsp}{vegetable oil}
	Meanwhile, heat the oil in now-empty Dutch oven over medium heat until 
	shimmering. Add garlic and onion and cook. stirring frequently, until deep brown 
	and onion is just starting to char on the edges, about 10 minutes.

	\ing[2]{tsp}{ground cumin}
	\ing[\fr12]{tsp}{ground cloves}
	\ing[2]{tsp}{dried oregano}
	\ing[1]{can}{chipotles in adobo}
	\ing[\fr14]{cup}{apple cider vinegar}
	\ing[2]{cups}{chicken stock}
	Add spices to the garlic and onions and stir constantly for about 30 seconds, until fragrant.
	Add three chipotle chiles and 2 tbsp of the sauce from the can, vinegar and remaining chicken stock. Make sure to scrape any brown
	bits from the bottom of the pan. Simmer until reduced by about half, then transfer all contents to
	a blender.

	\ing[2]{tsp}{fish sauce}
	Add the soaked chiles and liquid to the blender along with the fish sauce. Start blender on a low
	setting and slowly increase to high speed. Blend on high speed for 1 minute. The sauce should be a fine
	puree consistency.

	\ing[2]{tbsp}{vegetable oil}
	Heat oil in the Dutch oven over medium-high heat. Once oil is hot, sear both sides of the roast for
	1-2 minutes until deeply browned but not burnt.
	
	\ing[2]{}{bay leaves}
	Maintaining the medium-high heat, pour blended sauce into the Dutch oven over the meat. Agitate some, ensuring some of the sauce
	is able to get under the meat. Add bay leaves on top of the meat. Allow sauce to come to a gentle boil. Cover with the Dutch
	oven's lid slightly ajar.

	\newstep
	Transfer to the oven and cook for about 4 hours, flipping every 45 to 60 minutes, or until a cake tester or skewer inserted into
	the meat encounters little-to-no resistance. 
	
	\newstep
	Remove the meat from the Dutch oven and place on a cutting board. Remove and discard the bay leaves.
	Bring the remaining sauce to a gentle boil over medium-high heat until it has reduced to about 1.5 cups.

	\newstep
	Pull the meat into large chunks using two forks, discarding any fat if desired. Place in a sealable container and 
	add as much sauce as desired, depending on the size of the roast. Ideally, seal the container and
	refridgerate for at least a day. Otherwise, serve immediately.
	
\end{recipe}

\newpage

\begin{recipe}{Mexican Lasagna}{}{}
	
	
	Preheat oven to 350\0F.
	
	\ing[1]{lb}{ground meat (beef, pork, and/or substitute)}
	Cook meat in a large skillet/pan on medium-high heat until browned. Drain fat.
	
	\ing{15-oz can}{Ranch Style beans with jalape\~nos}
	\ing{4-oz can}{diced green chiles (hot)}
	\ing[1]{tsp}{garlic powder}
	\ing[1]{tsp}{ground cumin}
	\ing[\fr12]{tsp}{salt}
	\ing[\fr12]{tsp}{ground black pepper}
	Add ingredients to the skillet with cooked meat. Stir to combine, and cook until thoroughly heated. Reduce heat to low to keep warm.
	
	\ing{10-oz. can}{cream of mushroom soup}
	\ing{10-oz. can}{cream of celery soup}
	\ing{10-oz. can}{red enchilada sauce}
	Add ingredients to a saucepan over medium heat and stir to combine. Cook until thoroughly heated. 
	
	\ing[12]{}{small corn tortillas}
	Break 9 of the tortillas in half, keeping 3 whole.
	
	\ing[1]{lb}{cheese (jack and/or cheddar)}
	Shred all of the cheese. Reserve a handful for topping. 
	
	\newstep
	Grease the inside of a 13-\X9-inch baking dish.
	
	\newstep
	Spoon \fr13 of the sauce to the baking dish and spread evenly. Form a layer of tortillas by placing 6 of the tortilla halves around the perimeter of the baking dish (flat side touching the edge of the dish) and a whole tortilla in the center.
	
	\newstep
	Spoon \fr12 of the meat/bean mixture onto the tortillas, forming an even layer. Spoon another \fr13 of the sauce over the meat/bean mixture. Add \fr12 of the cheese on top.
	
	\newstep
	Add another layer of tortillas, meat/bean mixture, and cheese.
	
	\newstep
	Add the last layer of tortillas. Top with cheese.
	
	\newstep
	Bake for 30 minutes. 
	
	\newstep
	(optional) Top with guacamole or avocado slices, tomato, green onion, sour cream, etc.
	
\end{recipe}

\newpage

\section{Cocktails}

\begin{recipe}{Margarita}{}{}
  \ing[1\fr12]{oz}{blanco tequila}
  \ing[\fr12]{oz}{Grand Marnier}
  \ing[\fr34]{oz}{fresh lime juice}
  \ing[\fr12]{oz}{simple syrup}
  Add ingredients to cocktail shaker with ice.

  \ing[]{}{salt}
  (optional) Apply lime juice to outside rim of glass, and cover with salt.

  \newstep
  Shake cocktail shaker VERY WELL for at least 20 seconds.

  \newstep
  Strain into glass.
\end{recipe}

\begin{recipe}{Lemon Drop Martini}{}{}
  \ing[2]{oz}{vodka}
  \ing[\fr12]{oz}{triple sec}
  \ing[1]{oz}{fresh lemon juice}
  \ing[1]{oz}{simple syrup}
  Add ingredients to cocktail shaker with ice.

  \ing[]{}{sugar}
  (optional) Apply lemon juice to outside rim of glass, and cover with sugar.

  \newstep
  Shake cocktail shaker VERY WELL for at least 20 seconds.

  \newstep
  Strain into glass.
\end{recipe}

\end{document}
